Manuscript

### 2014-10-13 inst/simulation/manuscript.Rmd
...

@@

```{r figure-3-init-10days}
study <- getStudy(scenario="A") # Get study object, scenario doesn't matter
validation <- Validation(study=study, populationSizeOverEstimate=populationSizeOverEstimate)
populationSizes10days <- validation$getValidationTemporalPopulationSizes(scenarios=paste0(scenarios, "10days"), modelNames=modelNames)
validation$summarizePopulationSize(populationSizes10days)

@@

```{r table-2}
study <- getStudy(scenario="A")
validation <- Validation(study=study, populationSizeOverEstimate=populationSizeOverEstimate)
failedEstimations <- validation$countFailedEstimations(modelNames=modelNames)
failedEstimations$pFailed <- (1 - failedEstimations$nEstimated / 50) * 100
failedEstimations
```

>>>>

```{r figure-4-init}
getPopulationCorrelations <- function(modelName) {
  study <- getStudy(scenario="A")
  validation <- Validation(study=study, populationSizeOverEstimate=Inf)
  populationCorrelations <- validation$getValidationSpatialPopulationSizes(modelNames=modelName)
  return(populationCorrelations)
}

plotPopulationCorrelations <- function(populationCorrelations) {
  p <- ggplot(populationCorrelations, aes(True, Correlation)) + geom_point(size=1, colour="black") +
  facet_wrap(~Scenario, ncol=2) + xlab("True population size") +
  theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent"))#, axis.text.x=element_text(angle=45, hjust=.5, vjust=1))
  return(p)
}
```

```{r figure-4abc}
pc1 <- getPopulationCorrelations(scenarios=scenarios, modelName=modelNames[1])
pc2 <- getPopulationCorrelations(scenarios=paste0(scenarios, "combined"), modelName=modelNames[1])
pc3 <- getPopulationCorrelations(scenarios=paste0(scenarios, "10days"), modelName=modelNames[1])

p1 <- plotPopulationCorrelations(p1)
saveFigure(p1, "manuscript-figure-4a.png", width=4, height=4)
plotPopulationCorrelations(p2)
p2 <- saveFigure(p2, "manuscript-figure-4b.png", width=4, height=4)
plotPopulationCorrelations(p3)
p3 <- saveFigure(p3, "manuscript-figure-4c.png", width=4, height=4)
```

@@

```{r figure-3-init-10days, eval=FALSE}
study <- getStudy(scenario="A") # Get study object, scenario doesn't matter
validation <- Validation(study=study, populationSizeOverEstimate=populationSizeOverEstimate)
populationSizes10days <- validation$getValidationTemporalPopulationSizes(scenarios=paste0(scenarios, "10days"), modelNames=modelNames)
validation$summarizePopulationSize(populationSizes10days)

@@

```{r table-2, eval=FALSE}
# TODO: Combine with table 1
study <- getStudy(scenario="A")
validation <- Validation(study=study, populationSizeOverEstimate=populationSizeOverEstimate)
failedEstimations <- validation$countFailedEstimations(modelNames=modelNames)
failedEstimations$pFailed <- (1 - failedEstimations$nEstimated / 50) * 100
failedEstimations
```
